NGO analysis

### 2022-07-31 Dashboard/NGO Analysis dashboard alpha v003.Rmd
Making download button and report reactive.

```{r sidebar_button}
# download button - using uiOutput() because of an apparent bug
uiOutput("downloadUI")
```

@@

```{r reactive_plots, include=FALSE}
# Beginning of the second reactive chunk =======================================
# It's necessary to split the observers into separate parts, with all necessary
# code duplicated, because of R's limitations.

@@

>>>>

```{r sidebar_button}
# download button - using uiOutput() because of an apparent bug
# button and report are created in the second reactive chunk
uiOutput("downloadUI")
```

@@

```{r reactive_report_plots, include=FALSE}
# Beginning of the second reactive chunk =======================================
# It's necessary to split the observers into separate parts, with all necessary
# code duplicated, because of R's limitations.

@@

  # Report Output ==============================================================

  ## Download button -----------------------------------------------------------
  output$downloadUI <- renderUI({
    if (available_excel() && available_html()) {
      downloadButton("report", "Download report")
    }
  })

  ## Data exists condition testing----------------------------------------------
  # Essentially pretty random tests to connect to the individual
  # validate() functions upstream in the reactive chain

  # Excel
  available_excel <- reactive({
    TRUE
  }) |>
    bindEvent(setequal(
      names(exceldata()),
      c("year", "firm", "category", "sub_category", "name", "value")
    ))

  # HTML
  available_html <- reactive({
    TRUE
  }) |> bindEvent("lederlonn" %in% names(htmldata()))

  ## Report download and parameters --------------------------------------------
  output$report <- downloadHandler(

      # R Markdown render
      rmarkdown::render(tempReport,
        output_file = file,
        params = params,
        envir = new.env(parent = globalenv())
      )
    }
  )
